Towards a Cognitive System That Can Recognize Spatial Regions Based on Context

### 2012-01-24 scenarios/cdsr/trunk/papers/AAAI2012/evaluation.tex
updated robot related work
abstract tweaked, inset added to image

To determine how non-experts define CDRSs, we asked \textbf{SOMENUMBER} of users to draw polygons for each region type for each room. This task was performed using a webpage (link removed for blind review) on which each user was presented with an image of the real room plus the map data generated by the robot (as in Figure~\ref{fig:rooms}) onto which the drawing could be done. Users were also shown a polygon drawn by another user and asked to determine if it was an acceptable depiction of the region. All users provided acceptable regions, and therefore, we define the \textit{target region} as the union of the user-defined polygons. The user-provided data provides the ground truth against which we evaluate our transfers.

@@

\from{Nick}{Would this be just a single region type or averaging across all applicable ones?}
\from{Klenk}{This is averaging across all applicable ones.}

>>>>

To determine how non-experts define CDRSs, we asked \textbf{SOMENUMBER} of users to draw polygons for each region type for each room. This task was performed using a webpage (link removed for blind review) shown in the inset in Figure~\ref{fig:ug40} on which each user was presented with an image of the real room plus the map data generated by the robot (as in Figure~\ref{fig:rooms}) onto which the drawing could be done. Users were also shown a polygon drawn by another user and asked to determine if it was an acceptable depiction of the region. All users provided acceptable regions, and therefore, we define the \textit{target region} as the union of the user-defined polygons. The user-provided data provides the ground truth against which we evaluate our transfers.

@@
